InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-29 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>
Update paper.tex
Co-authored-by: RaphaW <116720366+RaphaW@users.noreply.github.com>
Fix citation
add short text

@@

The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 finetuned on the AI or Not dataset. swin-tiny-patch4-window7-224 by microsoft is a new vision Transformer \cite{https://arxiv.org/pdf/2103.14030.pdf}.

>>>>

\textbf{Winston AI} is a commertial AI text detector that starts at 18\$ a month. The two primary methods for checking if a text is AI written is firstly Linguistic analysis. Linguistic analysis analyses every text of its characteristics like repetitivness. These characteristics are different between AI and humans. The other is Data Training, where the detector saw many AI written texts of one model and learned unice characteristics that this model uses which than can be detected.\cite{Winston AI}

@@
